Community Embeddings for Friend Suggestions

### 2020-10-12 conference_101719.tex
next: Facebook Friend Suggestions
FFS intro

>>>>

\section{Facebook Friend Suggestions}

The recommender system based on community embeddings with the Bayesian Gaussian mixture model and variational inference is quantitatively evaluated. Friend suggestions are generated for the \citetitle{social_circles_fb} dataset \cite{social_circles_fb, social_circles_in_ego_networks}.

The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the \citetitle{social_circles_fb} graph. Both Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} are evaluated. The top-$N$ recommendations are evaluated by the hit-rate metric.
